This paper contributes a reproducible public-trace benchmark for predictive autoscaling that spans aggregate, machine-level, transfer, and broad service-level evidence. The aggregate and machine-cohort benchmarks show that linear regression remains the strongest point-forecast baseline, while the uncertainty-aware \texttt{UA-MSTCN-Lite} surrogate contributes calibrated upper quantiles that are useful for predictive control. Across the audited 139-service broad cohort, the service-level point-forecast headline also shifts to linear regression.

The central contribution is therefore a benchmark and boundary-mapping result rather than a new controller architecture. On the aggregate trace, predictive control still reduces over-provisioning substantially relative to the reactive threshold baseline. Across the audited broad service cohort, however, predictive control raises mean SLA violation and mean scaling actions relative to reactive control under equal-weighted service averaging, while the apparent mean over-provisioning reduction is not stable under paired service bootstrap. These mixed and negative service-level findings are scientifically valuable because they show that the earlier targeted headline was not robust and they identify where a shared global predictive policy breaks down under service heterogeneity instead of masking that boundary behind aggregate improvements.

The most valuable next steps are now narrower and more concrete than simple cohort expansion. First, service-aware tuning should be evaluated under a held-out-service protocol so that any policy gain is demonstrated without service-selection leakage. Second, a stronger temporal backbone should be tested against the same linear and persistence baselines to determine whether the point-forecast gap can be closed without sacrificing reproducibility.
