\paragraph{Funding}
The author received no specific funding for this study.

\paragraph{Competing interests}
The author declares no competing interests.

\paragraph{Ethics approval and consent to participate}
Not applicable.

\paragraph{Consent for publication}
Not applicable.

\paragraph{Data availability}
The raw Alibaba Cluster Trace Program datasets are publicly available from the Alibaba Cluster Trace Program repository. The submitted manuscript version is maintained in a private GitHub review repository together with a frozen review-freeze package that includes processed datasets, cohort summaries, result tables, figure-generation artifacts, and manuscript sources. Access can be granted to the editor and reviewers during peer review. Upon acceptance, the same frozen package will be deposited in a public repository with a persistent identifier.

\paragraph{Materials availability}
Not applicable.

\paragraph{Code availability}
The scripts used for preprocessing, forecasting, broad service-cohort construction, and policy evaluation are maintained in the same private GitHub review repository and frozen review-freeze package. Access can be granted to the editor and reviewers during peer review. Upon acceptance, the same code package will be deposited in the same public repository with a persistent identifier.

\paragraph{Author contribution}
Jinchun Liu conceived the study, designed the methodology, implemented the experiments, analyzed the results, and wrote the manuscript.
